---
title: ""
output: 
  html_document: 
    theme: sandstone
    toc: yes
    toc_depth: 1
    toc_float: yes
    keep_md: yes
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: 0px;
  margin-right: 0px
}
</style>

<h1><center>Boar Stud Master Report</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#------------------Source Libraries and Scripts-----------------------#

library(tidyverse)
library(knitr)
library(dplyr)
library(lubridate)
library(stringr)
library(DT)
library(readr)
library(here)
library(kableExtra)

##MODIFY Cull.R and GCard2.R to add weeks for removal reason errors###

# source(here::here("scripts","14day.R"))
# source(here::here("scripts","Batch.R"))
# source(here::here("scripts","Break.R"))
# source(here::here("scripts","Distribution.R"))
# source(here::here("scripts","Inventory.R"))
# source(here::here("scripts","Lut.R"))
# source(here::here("scripts","Met.R"))
# source(here::here("scripts","Mort.R"))
# source(here::here("scripts","Non.R"))
# source(here::here("scripts","PPP.R"))
# source(here::here("scripts","Rest.R"))
# source(here::here("scripts","SQC.R"))
# source(here::here("scripts","Train.R"))
# source(here::here("scripts","Cull.R")) ## RUN INDIVIDUALLY AND CHANGE DATES, ONLY RUN ONCE PER WEEK ##
# source(here::here("scripts","NTC.R"))
# source(here::here("scripts","Bottom.R"))
# source(here::here("scripts","nucleus.R"))
# source(here::here("scripts","Cond.R"))
# source(here::here("scripts","Hours.R"))
# source(here::here("scripts","Mort2.R"))
# 
# # ### MAKE SURE CULL FILE DATES HAVE BEEN FIXED###
# 
# source(here::here("scripts","PCard2.R"))
# source(here::here("scripts","GCard2.R"))
# source(here::here("scripts","Scard.R"))
# source(here::here("scripts","Dash2.R"))


```

<br>

<h2><center>`r year(floor_date(today(),unit = "week",week_start = 5))` Week `r isoweek(floor_date(today(),unit = "week", week_start = 1)-7)`</h2>

<br>
<br>
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dashboard1<-read_csv(here::here("data","dash2.csv"))

dashboard1<-dashboard1[order(-dashboard1$`13 Week Total Score`),]

kbl(x = dashboard1, align = 'c', digits = 1) %>%
  column_spec(2,background = ifelse(is.na(dashboard1$`Semen QCQA Score`),"white",
                                    ifelse(dashboard1$`Semen QCQA Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`Semen QCQA Score`>6.99,"yellow","red"))))  %>%
  column_spec(3,background = ifelse(is.na(dashboard1$`13 Week Semen QCQA Score`),"white",
                                    ifelse(dashboard1$`13 Week Semen QCQA Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`13 Week Semen QCQA Score`>6.99,"yellow","red")))) %>%
  column_spec(4,background = ifelse(is.na(dashboard1$`Production Score`),"white",
                                    ifelse(dashboard1$`Production Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`Production Score`>6.99,"yellow","red"))))  %>%
  column_spec(5,background = ifelse(is.na(dashboard1$`13 Week Production Score`),"white",
                                    ifelse(dashboard1$`13 Week Production Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`13 Week Production Score`>6.99,"yellow","red")))) %>%
  column_spec(6,background = ifelse(is.na(dashboard1$`Genetic Implementation Score`),"white",
                                    ifelse(dashboard1$`Genetic Implementation Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`Genetic Implementation Score`>6.99,"yellow","red")))) %>%
  column_spec(7,background = ifelse(is.na(dashboard1$`13 Week Genetic Implementation Score`),"white",
                                    ifelse(dashboard1$`13 Week Genetic Implementation Score`>8.99,"limegreen",
                                           ifelse(dashboard1$`13 Week Genetic Implementation Score`>6.99,"yellow","red")))) %>%
  column_spec(8,background = ifelse(is.na(dashboard1$`Total Score`),"white",
                                    ifelse(dashboard1$`Total Score`>26.99,"limegreen",
                                           ifelse(dashboard1$`Total Score`>20.99,"yellow","red")))) %>%
  column_spec(9,background = ifelse(is.na(dashboard1$`13 Week Total Score`),"white",
                                    ifelse(dashboard1$`13 Week Total Score`>26.99,"limegreen",
                                           ifelse(dashboard1$`13 Week Total Score`>20.99,"yellow","red")))) %>%
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Semen Scorecard</h1>


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
sscorecard1<-read_csv(here::here("data","scard2.csv"))
sscorecard2<-read_csv(here::here("inputs","semkey.csv"))

sscorecard1<-sscorecard1[order(-sscorecard1$`13 Week Average`,-sscorecard1$Total),]

kbl(x = sscorecard1, align = 'c', digits = 1) %>%
  column_spec(4,background = ifelse(sscorecard1$CScore>3.99,"limegreen",
                                    ifelse(sscorecard1$CScore>2.99,"yellow",
                                           ifelse(sscorecard1$CScore>1.99, "orange","red")))) %>%
  column_spec(6,background = ifelse(sscorecard1$MScore>2.99,"limegreen",
                                    ifelse(sscorecard1$MScore>1.99,"yellow","red"))) %>%
  column_spec(8,background = ifelse(sscorecard1$AScore>1.99,"limegreen",
                                    ifelse(sscorecard1$AScore>0.99,"yellow","red"))) %>%
  column_spec(10,background = ifelse(sscorecard1$BScore>0.99,"limegreen","red")) %>%
  column_spec(12,background = ifelse(sscorecard1$`4 Week Average`>8.99,"limegreen",
                                    ifelse(sscorecard1$`4 Week Average`>6.99,"yellow","red"))) %>%
  column_spec(13,background = ifelse(sscorecard1$`13 Week Average`>8.99,"limegreen",
                                    ifelse(sscorecard1$`13 Week Average`>6.99,"yellow","red"))) %>% 
  kable_styling(full_width = T,
                font_size = 14)

kbl(sscorecard2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Production Scorecard</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
pscorecard1<-read_csv(here::here("data","pcard2.csv"))

pscorecard1<-pscorecard1[order(-pscorecard1$`4 Week Average`,-pscorecard1$Total),]

kbl(x = pscorecard1, align = 'c', digits = 2) %>%
  column_spec(3,background = ifelse(pscorecard1$TScore>2.99,"limegreen","red")) %>%
  column_spec(5,background = ifelse(pscorecard1$RScore>2.99,"limegreen",
                                    ifelse(pscorecard1$RScore>1.99,"yellow","red"))) %>%
  column_spec(7,background = ifelse(pscorecard1$PScore>1.99,"limegreen","red")) %>%
  column_spec(9,background = ifelse(pscorecard1$LScore>1.99,"limegreen",
                                    ifelse(pscorecard1$LScore>0.99,"yellow","red"))) %>%
  column_spec(11,background = ifelse(pscorecard1$`4 Week Average`>8.99,"limegreen",
                                    ifelse(pscorecard1$`4 Week Average`>6.99,"yellow","red"))) %>%
  column_spec(12,background = ifelse(pscorecard1$`Quarter Average`>8.99,"limegreen",
                                    ifelse(pscorecard1$`Quarter Average`>6.99,"yellow","red"))) %>%
  kable_styling(full_width = T,
                font_size = 14)


pscorecard3<-read_csv(here::here("inputs","prodkey.csv"))
kbl(pscorecard3) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Genetic Implementation Scorecard</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gscorecard1<-read_csv(here::here("data","gcard2.csv"))

gscorecard1<-gscorecard1[order(-gscorecard1$`4 Week Average`,-gscorecard1$Total),]

kbl(x = gscorecard1, align = 'c', digits = 2) %>%
  column_spec(3,background = ifelse(gscorecard1$IScore>3.99,"limegreen",
                                    ifelse(gscorecard1$IScore>2.99,"yellow",
                                           ifelse(gscorecard1$IScore>1.99,"orange", "red")))) %>%
  column_spec(5,background = ifelse(gscorecard1$TScore>2.99,"limegreen",
                                    ifelse(gscorecard1$TScore>1.99,"yellow","red"))) %>%
  column_spec(7,background = ifelse(gscorecard1$RScore>1.99,"limegreen",
                                    ifelse(gscorecard1$RScore>0.99, "yellow","red"))) %>%
  column_spec(9,background = ifelse(gscorecard1$CScore>0.99,"limegreen","red")) %>%
  column_spec(11,background = ifelse(gscorecard1$`4 Week Average`>8.99,"limegreen",
                                    ifelse(gscorecard1$`4 Week Average`>6.99,"yellow","red"))) %>%
  column_spec(12,background = ifelse(gscorecard1$`Quarter Average`>8.99,"limegreen",
                                    ifelse(gscorecard1$`Quarter Average`>6.99,"yellow","red"))) %>%
  kable_styling(full_width = T,
                font_size = 14)

gscorecard3<-read_csv(here::here("inputs","genkey.csv"))
kbl(gscorecard3) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Boar Stud Summary</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#------------------------------Table 1---------------------#

table1a<-read_csv("C:/Users/vance/Documents/projects/Working Project Directory/data/data-SQL-BS-Data-Pull/dates.csv")
table1b <- read_csv(here::here("data","inventoryex.csv"))
table1c <- read_csv(here::here("data","dist1.csv"))

table1a$`Collection Date`<-as.Date(table1a$`Collection Date`)
table1a$`Distribution Date`<-as.Date(table1a$`Distribution Date`)

table1d<-left_join(x = table1a,y = table1b,by=c("Boar Stud"="Boar Stud"))
table1e<-left_join(x = table1d,y = table1c,by=c("Boar Stud"="Boar Stud"))

table1f<-table1e %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))

kbl(table1f) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
breakdown <- read_csv(here::here("data","breakdown.csv"))

breakdown1<-breakdown %>% 
  group_by(`Boar Stud`,Breed.x) %>%
  filter(Distributed=='YES') %>% 
  summarise('Boars Distributed'=n_distinct(BoarID))

breakdown2<-breakdown %>% 
  group_by(`Boar Stud`,Breed.x) %>% 
  filter(Collected=='YES',
         `Collection Status`=='US',
         Distributed=='NO') %>% 
  summarise('Boars Spilled'=n_distinct(BoarID))

breakdown3<-breakdown %>% 
  group_by(`Boar Stud`,Breed.x) %>% 
  filter(Collected=='NO') %>% 
  summarise('Boars Not Collected'=n_distinct(BoarID))

breakdown4<-read_csv(here::here("data","cont.csv"))

breakdown5<-left_join(x = breakdown1,y = breakdown2,by=c("Boar Stud"="Boar Stud","Breed.x"="Breed.x"))

breakdown6<-left_join(x = breakdown5,y = breakdown3,by=c("Boar Stud"="Boar Stud","Breed.x"="Breed.x"))

breakdown7<-left_join(x = breakdown6,y = breakdown4,by=c("Boar Stud"="Boar Stud.x","Breed.x"="Breed.x"))

breakdown7[is.na(breakdown7)]<-0

```

<br>
<br>
<br>

<h1>Boar Training - Current Performance</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table5a<-read_csv(here::here("data","train.csv"))
table5b<-table5a %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))

kbl(table5b,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Boar Training - 2 Week Performance</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table6a<-read_csv(here::here("data","trained.csv"))
table6b<-table6a %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))

kbl(table6b,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Removal Reason Error Boars - Production</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table23a<-read_csv(here::here("data","sqntboars.csv"))

table23b<-table23a %>% 
  filter(DESCR=='SEMEN QUALITY',
         `Collections Trashed Consecutively`<6 | is.na(`Collections Trashed Consecutively`))

table23c<-table23a %>% 
  filter(DESCR=='WILL NOT TRAIN',
         `Consecutive Failed Collections`<8 | is.na(`Consecutive Failed Collections`))

table23d<-rbind(table23b,table23c)

table23e<-table23d[c(1:4,6,12,13,14)]

kbl(table23e,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Removal Reason Error Boars - Index</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table24a<-read_csv(here::here("data","indexcullerrorboars.csv"))

table24b<-table24a %>% 
  filter(Date_Studout>=floor_date(x = today(),unit = "week",week_start = 1)-28)

table24c<-table24b[c(1,2,3,6,8,11,15)]

kbl(table24c,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Lutalyse Usage</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table8a<-read_csv(here::here("data","lut.csv"))
table8b<-table8a %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))

kbl(table8b,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Non-Working Boars</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table9a<-read_csv(here::here("data","non.csv"))
table9b<-table9a %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))
kbl(table9b,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)

```

<br>
<br>
<br>

<h1>Post Production Performance</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table10a<-read_csv(here::here("data","ppm.csv"))

kbl(table10a,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Semen Quality Culls</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table11a<-read_csv(here::here("data","sqc.csv"))
table11b<-table11a %>% 
  filter(!`Boar Stud`%in%c('Ingold','Clinton'))

kbl(table11b, align = 'c') %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Boar Training Culls</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table12a<-read_csv(here::here("data","ntc.csv"))

kbl(table12a, align = 'c') %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Low Index Culling</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table13a<-read_csv(here::here("data","cull.csv"))

table13a$WeekCommencing<-as.Date(table13a$WeekCommencing, format="%m/%d/%Y")

table13b<-table13a %>% 
  filter(WeekCommencing>=floor_date(x = today(),unit = "week",week_start = 7)-91) %>% 
  group_by(`Boar Stud`) %>% 
  summarise('Total Boars Culled' =sum(`Boars Culled`))

table13c<-table13a %>% 
  filter(WeekCommencing>=floor_date(x = today(),unit = "week",week_start = 7)-91) %>% 
  group_by(`Boar Stud`) %>% 
  summarise('Total Low Index Boars Culled' =sum(`Low Index Culls`))

table13d<-table13a %>% 
  group_by(`Boar Stud`) %>% 
  filter(WeekCommencing==max(WeekCommencing))

table13d$`Most Recent Culls`<-table13d$WeekCommencing

table13e<-left_join(x = table13b,y = table13c,by=c("Boar Stud"="Boar Stud"))
table13f<-left_join(x = table13e,y = table13d,by=c("Boar Stud"="Boar Stud"))

table13f<-table13f[c(1,2,3,7,4,5)]

kbl(table13f, align = 'c') %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Bottom 1% - SPG240</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table14a<-read_csv(here::here("data","bottom.csv"))

table14b<-table14a %>% 
  filter(Breed=='SPG240',
         rankp<=0.01) %>% 
  arrange(rank)

table14c<-table14b[c(1:5,8,9)]

kbl(table14c,align = 'c', digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>4-Week Concentrations</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table17a<-read_csv(here::here("data","scarddata2.csv"))

table17b<-table17a %>%
  filter(StudName%in%c('7362','ASKI','WILL','ROBE','DEER','LAUR','MACO','CIMA','CYCL','SKYL','YUMA')) %>% 
  group_by(`Boar Stud`) %>% 
  top_n(n = 4,wt = yearweek)
  
  
  

table17b<-table17b[c(15,4,2)]

table17c<-table17b %>% 
  group_by(`Boar Stud`) %>% 
  spread(key = yearweek,value = `Average Concentration`)

kbl(table17c,align = 'c') %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Blood Diagnostic Errors</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table18a<-read_csv(here::here("inputs","diag.csv"))

table18b<-table18a[c(1,2,9,10)]

table18c<-table18b %>% 
  mutate('PTotal'=(1-(Total/Submissions))*100)

table18d<-table18c[c(1,2,5)]

table18e<-table18d %>% 
  group_by(`Boar Stud`) %>% 
  filter(!`Boar Stud`%in%c('Princeton','High Desert','SPG TX')) %>% 
  top_n(n = 13,wt = Yearweek) %>% 
  spread(key = Yearweek,value = PTotal)

table18f<-table18b %>% 
  group_by(`Boar Stud`) %>% 
  top_n(n = 13,wt = Yearweek) %>% 
  mutate('13 Week Average'=(1-((sum(Total)/sum(Submissions))))*100)

table18f<-table18f[!duplicated(table18f$`Boar Stud`),]

table18g<-left_join(x = table18e,y = table18f, by=c("Boar Stud"="Boar Stud"))

table18g<-table18g[-c(15,16,17)]

kbl(x = table18g, align = 'c', digits = 1) %>%
  column_spec(15,background = ifelse(table18g$`13 Week Average`>92.99,"limegreen","red")) %>%
  kable_styling(full_width = T,
                font_size = 14)
  
```

<br>
<br>
<br>

<h1>Boars Per Batch</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table19a<-read_csv(here::here("data","batch.csv"))

table19a[is.na(table19a)]<-0

kbl(table19a,align = 'c') %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Metrosperm Readings</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table20a<-read_csv(here::here("data","met.csv"))

table20a$`% Unacceptable`<-((table20a$`Readings Under 0.100`+table20a$`Readings Over 0.300`)/table20a$`Number of Readings`)*100

kbl(table20a, align = 'c', digits = 3) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Extender Conductivity</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table21a<-read_csv(here::here("data","cond.csv"))

kbl(table21a,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```

<br>
<br>
<br>

<h1>Hours/Boar/Week</h1>

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
table22a<-read_csv(here::here("data","hours.csv"))

kbl(table22a,align = 'c',digits = 2) %>% 
  kable_styling(full_width = T,
                font_size = 14)
```
